First SOC budget analysis

### 2020-06-16 ResultNotebooks/results_SOCflows.Rmd
Update result scripts to new structure

---
  title: "First SOC budget analysis"
output:
  html_document:
  df_print: paged
pdf_document: default
---

```{r load}
library(moinput)
library(mrvalidation)
library(socbudget)
library(magpiesets)

#input       <- "/home/kristine/WORK/R libraries/rd3mod_inputdata/output/rev1_690d3718e151be1b450b394c1064b1c5_validation.tgz"
#inputfolder <- gsub("[^/]*$","", input)
#untar(input, inputfolder)

setConfig(cachefolder = "/home/kristine/WORK/R libraries/rd3mod_inputdata/cache/rev4.43_SOC_0.5.0/", forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")

>>>>

---
  title: "First SOC budget flow analysis"
output:
  html_document:
  df_print: paged
pdf_document: default
---

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev <- "rev0.6_mrSOC"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

```{r load data}

files <- list.files("Data")

CarbonInput      <- readRDS("Data/CarbonInput.rds")
CarbonLitter     <- readRDS("Data/CarbonLitter.rds")
CarbonManure     <- readRDS("Data/CarbonManure.rds")           
CarbonResidues   <- readRDS("Data/CarbonResidues.rds")
CarbonHarvest    <- readRDS("Data/Crop_Harvest.rds")
SoilCarbon       <- readRDS("Data/SoilCarbon.rds")

Landuse          <- readRDS("Data/Landuse.rds")
LanduseChange    <- readRDS("Data/LanduseChange.rds")

FAOmassbalance   <- readRDS("Data/FAOmassbalance_ISO.rds" )
ManureExcreted   <- readRDS("Data/Manure_excreted.rds")
ManureRecycled   <- readRDS("Data/Manure_recycled.rds")
ResidueBiomass   <- readRDS("Data/Residue_Biomass.rds")
ResiduesAgDemand <- readRDS("Data/ResiduesAg_FieldBalance.rds")

### 2020-06-16 ResultNotebooks/results_SOCtesting.Rmd
Update result scripts to new structure

```{r load data}
library(moinput)
library(mrvalidation)
library(socbudget)

setConfig(cachefolder = "/home/kristine/WORK/R libraries/rd3mod_inputdata/cache/rev4.43_SOC_0.5.0/", forcecache = TRUE)
#setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43_SOC_0.5.0/", forcecache = TRUE)
#setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43/", forcecache = TRUE)
#setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43/", forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
#setConfig(sourcefolder = "/home/kristine/WORK/R libraries/rd3mod_inputdata/sources/")

@@

@@

print(dimSums(reg_SOCStock, dim=1))
```
```{r barplot reg stock, out.width="100%", out.height=1000}

@@

mipBarYearData(reg_SOCStock)
```

@@

@@

    SOCDens_lut <- dimSums(SoilCarbon[,,c("steadystate","actualstate")], dim=3.3)

@@

cropland_share <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)/dimSums(SoilCarbon[,,"actualstate"][,,"natveg"], dim=3)
cropland_share[Landuse[,,"crop"]==0] <- NA

@@

library(RColorBrewer)
cols      <- colorRampPalette(brewer.pal(11, "RdYlGn"))(1000)
outputdir <- "/home/kristine/WORK/Paper/historicalsocbudget/SOCbudgetPaper/images/maps/"

>>>>

```{r load data}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)

#setConfig(cachefolder = "/home/kristine/WORK/R libraries/rd3mod_inputdata/cache/rev4.43_SOC_0.5.0/", forcecache = TRUE)
setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43_mrSOC_0.4.1/", forcecache = TRUE)
#setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43/", forcecache = TRUE)
#setConfig(cachefolder = "/home/kristine/mnt/rd3mod/inputdata/cache/rev4.43/", forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
#setConfig(sourcefolder = "/home/kristine/WORK/R libraries/rd3mod_inputdata/sources/")

@@

print(mbind(dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=c(1,3)),
            dimSums(dimSums(SoilCarbon[,,"steadystate"], dim=3.3)* Landuse, dim=c(1,3))))

@@

print(dimSums(reg_SOCStock, dim=1))
```

```{r barplot reg stock, out.width="100%", out.height=1000}

@@

mipBarYearData(reg_SOCStock)
```
Plot global stocks

Plot cellular stocks

library(luplot)
library(magpiesets)

cellSOCdens   <- (dimSums(dimSums(SoilCarbon[,,"naturalstate"], dim=3.2) * Landuse, dim=c(3))/dimSums(Landuse, dim=c(3)))[,findset("past"),]
cellSOCdens[is.na(cellSOCdens)] <- 0

cellSoilGrids <- readSource("SoilGrids", subtype="cstock_0_30", convert="onlycorrect")
cellLPJml     <- calcOutput("LPJmL", version="LPJmL4", climatetype="CRU_4", subtype="soilc_layer", time="raw", selectyears="past", aggregate=FALSE)
cellLPJml     <- collapseNames(cellLPJml[,,"layer1"]+1/3*cellLPJml[,,"layer2"], collapsedim = c(2,3))

diffSoilGrids <- cellSOCdens - cellSoilGrids
diffLPJml     <- cellSOCdens - cellLPJml

luplot::plotmap(diffLPJml[,10,], legend_range = c(-80,80))
```

@@

    library(magpiesets)

@@

    SOCDens_lut <- dimSums(SoilCarbon[,,c("steadystate","actualstate","naturalstate")], dim=3.3) 
    SOCDens_lut[,,"naturalstate.crop"] <- SOCDens_lut[,,"actualstate.crop"]

@@

cropland_share <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)/dimSums(SoilCarbon[,,"naturalstate"][,,"natveg"], dim=3)
cropland_share[Landuse[,,"crop"]==0] <- NA

@@

library(RColorBrewer)
cols      <- colorRampPalette(brewer.pal(11, "RdYlGn"))(7)[]
outputdir <- "/home/kristine/WORK/Paper/historicalsocbudget/SOCbudgetPaper/images/maps/"
